Co-citations in context

### 2019-06-12 cocit_r.tex
edited terminal Introduction

Our analyses, using multiple techniques, provides substantial evidence that constraining the reference substitutions to the disciplinary subnetwork reduces model misspecification compared to treating all substitutions within WoS as equiprobable. 
Furthermore, re-analyses of these three semantically-themed
 citation networks  under the improved model reveals strikingly different trends than those 
 observed by Uzzi {\em et al.} 
 For example, while Uzzi {\em et al.}~claimed that highly cited articles are more likely to be both HC and HN than expected, and that this trend held across all subdisciplines, we find that these trends vary with the subdiscipline so that no universal trends can be established. Specifically, 
 HC remains highly correlated with highly cited articles in the immunology and metabolism datasets but not with applied physics, and HN is highly correlated with highly cited articles in applied physics but not with immunology and metabolism.    
 Thus, disciplinary networks are different from each other, and trends that hold for the full WoS network do not hold for even large subnetworks (such as metabolism). 
 Furthermore, we also found that the categories HC, HN, etc.,  demonstrating the highest percentage of highly cited articles are not robust with respect to varying thresholds for high citation counts or for highly novel citation patterns.
 Overall, our study, although limited to three disciplinary subnetworks, suggests that  co-citation analysis, while useful in many regards, cannot be used to provide universal features in scholarship, due to important differences between disciplines and between publications.

>>>>

Our analyses, using multiple techniques, provides substantial evidence that constraining the reference substitutions to the disciplinary subnetwork reduces model misspecification compared to treating all substitutions within WoS as equiprobable. 
Furthermore, re-analyses of these three semantically-themed
 citation networks  under the improved model reveals strikingly different trends than those 
 observed by Uzzi {\em et al.} 
 For example, while Uzzi {\em et al.}~claimed that highly cited articles are more likely to be both HC and HN than expected, and that this trend held across all subdisciplines, we find that these trends vary with the subdiscipline so that no universal trends can be established. Specifically, 
 HC remains highly correlated with highly cited articles in the immunology and metabolism datasets but not with applied physics, and HN is highly correlated with highly cited articles in applied physics but not with immunology and metabolism.    
 Thus, disciplinary networks are different from each other, and trends that hold for the full WoS network do not hold for even large subnetworks (such as metabolism). 
 Furthermore, we also found that the categories HC, HN, etc.,  demonstrating the highest percentage of highly cited articles are not robust with respect to varying thresholds for high citation counts or for highly novel citation patterns.
 Overall, our study, although limited to three disciplinary subnetworks, suggests that  co-citation analysis, while useful in many regards, may not be very useful in detecting universal features of impactful publications, due to important differences between disciplines and between publications.
